Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-12 doc/JFLA2022/paper.tex
input paper.bbl in paper.tex
add snippets in the JFLA200 directory
fix a few typos

\usepackage{texments}
%%% for movies by alectryon
\usepackage{./assets/alectryon}
\usepackage{./assets/pygments}
%%% One hypothesis per line 
\makeatletter
\renewcommand{\alectryon@hyps@sep}{\alectryon@nl}
\makeatother

%%% \snippets{A,B,C,…} inputs a series of snippets as one block (with \itemsep
%%% between them).  A, B, C should be paths to files in snippets/.
\usepackage{etoolbox}
\makeatletter
\newcommand{\inputsnippets}[1]
  {{\setlength{\itemsep}{1pt}\setlength{\parsep}{0pt}% Adjust spacing
    \alectryon@copymacros\begin{io}
      \forcsvlist{\item\@inputsnippet}{#1}
    \end{io}}}
\let\input@old\input % Save definition of \input
\newcommand{\@inputsnippet}[1]
  {{\renewenvironment{alectryon}{}{}% Skip \begin{alectryon} included in snippet
    \input@old{snippets/#1}}}
\makeatother

@@

\begin{theorem}
  In the Hydra game, Hercules eventually wins, whichever the strategy of both players :
  choice of a head to chop off, choice of the number of copies. 
 \label{kp:thm1}
\end{theorem}

@@

\section{Recent developments}
The 2018 article~\cite{JFLA2018paper} presented a formal proof of  a variant of Theorem~\ref{kp:thm2}:

@@

\begin{figure}[h]
  \centering
  \fbox{
    \begin{minipage}[h]{1.0\linewidth}
 \inputsnippets{Hprime/HprimeDef}     
    \end{minipage}}
 \caption{$H'$ definition with the \texttt{coq-equations}
 plug-in~\cite{sozeau:hal-01671777}}
\label{fig:Hprime}
\end{figure}

@@

The \Hydras book is written in LaTeX, but it makes very frequent references (about once per page, 274 snippets over 281 pages) to parts of the \coq development, showing definitions (Fig.~\ref{fig:Hprime}), computation results (Fig.~\ref{fig:Pow-evalPow17LetIn}), lemmas (Fig.~\ref{fig:Ex42E0}) and parts of  proof scripts (Fig.~\ref{fig:Ex42-schutte}). The order in which these references appear in the book is independent of the structure of our libraries, so we chose to maintain the book as a standalone document, separate from the \coq source code.  This in contrast with the Coqdoc approach, where explanatory prose is embedded within \coq source files (a detailed discussion of various approaches to the documentation of \coq developments is in \cite{alectryonpaper}).

@@

   \begin{figure}[h]
     \centering
     \fbox{
       \begin{minipage}[h]{1.0\linewidth}
         \inputsnippets{Pow/evalPow17LetIn}
       \end{minipage}}
  \caption{\label{fig:Pow-evalPow17LetIn}Automatically capturing the output of computations}
\end{figure}

  \begin{figure}[h]
    \centering
    \fbox{
      \begin{minipage}[h]{1.0\linewidth}
        \inputsnippets{E0/Ex42}
      \end{minipage}}
    \caption{A simple proof by computation}
    \label{fig:Ex42E0}
  \end{figure}

@@

\inputsnippets{Schutte/Ex42a}

@@

\inputsnippets{Schutte/Ex42b}

@@

\inputsnippets{Schutte/Ex42d, %to remove if short paper
  Schutte/Ex42c, Schutte/Ex42e}

@@

\label{sect:bib}
\bibliographystyle{plain}
%\bibliographystyle{alpha}
%\bibliographystyle{unsrt}
%\bibliographystyle{abbrv}
\bibliography{../thebib}

>>>>

\usepackage{texments}
%%% for movies by alectryon
\usepackage{alectryon}
\usepackage{pygments}
%%% One hypothesis per line 
\makeatletter
\renewcommand{\alectryon@hyps@sep}{\alectryon@nl}
\makeatother

%%% \snippets{A,B,C,…} inputs a series of snippets as one block (with \itemsep
%%% between them).  A, B, C should be paths to files in snippets/.
\usepackage{etoolbox}
\makeatletter
\newcommand{\inputsnippets}[1]
  {{\setlength{\itemsep}{1pt}\setlength{\parsep}{0pt}% Adjust spacing
    \alectryon@copymacros\begin{io}
      \forcsvlist{\item\@inputsnippet}{#1}
    \end{io}}}
\let\input@old\input % Save definition of \input
\newcommand{\@inputsnippet}[1]
  {{\renewenvironment{alectryon}{}{}% Skip \begin{alectryon} included in snippet
    \input@old{#1}}}
\makeatother

@@

\begin{theorem}
  In the Hydra game, Hercules eventually wins, whichever the strategy of both players:
  choice of a head to chop off, choice of the number of copies. 
 \label{kp:thm1}
\end{theorem}

@@

\section{Recent developments}
The 2018 article~\cite{JFLA2018paper} presented a formal proof of the following theorem:

@@

\begin{figure}[h]
  \centering
  \fbox{
    \begin{minipage}[h]{1.0\linewidth}
 \inputsnippets{Hprime_HprimeDef}     
    \end{minipage}}
 \caption{$H'$ definition with the \texttt{coq-equations}
 plug-in~\cite{sozeau:hal-01671777}}
\label{fig:Hprime}
\end{figure}

@@

The \Hydras book is written in LaTeX, but it makes very frequent references (about once per page, 274 snippets over 281 pages) to parts of the \coq development, showing definitions (Fig.~\ref{fig:Hprime}), computation results (Fig.~\ref{fig:Pow-evalPow17LetIn}), lemmas (Fig.~\ref{fig:Ex42E0}) and parts of  proof scripts (Fig.~\ref{fig:Ex42-schutte}). The order in which these references appear in the book is independent of the structure of our libraries, so we chose to maintain the book as a standalone document, separate from the \coq source code.  This  contrasts with the Coqdoc approach, where explanatory prose is embedded within \coq source files (a detailed discussion of various approaches to the documentation of \coq developments can be found  in \cite{alectryonpaper}).

@@

   \begin{figure}[h]
     \centering
     \fbox{
       \begin{minipage}[h]{1.0\linewidth}
         \inputsnippets{Pow_evalPow17LetIn}
       \end{minipage}}
  \caption{\label{fig:Pow-evalPow17LetIn}Automatically capturing the output of computations}
\end{figure}

  \begin{figure}[h]
    \centering
    \fbox{
      \begin{minipage}[h]{1.0\linewidth}
        \inputsnippets{E0_Ex42}
      \end{minipage}}
    \caption{A simple proof by computation}
    \label{fig:Ex42E0}
  \end{figure}

@@

\inputsnippets{Schutte_Ex42a}

@@

\inputsnippets{Schutte_Ex42b}

@@

\inputsnippets{Schutte_Ex42d, %to remove if short paper
  Schutte_Ex42c, Schutte_Ex42e}

@@

\label{sect:bib}
\bibliographystyle{plain}
%\bibliographystyle{alpha}
%\bibliographystyle{unsrt}
%\bibliographystyle{abbrv}
\input{paper.bbl}

%\bibliography{../thebib}
